---
title: "Configuring lambdar"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Configuring lambdar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lambdar)
```

The `_lambdar.yml` file can be used to customise your container image. Lambdar tries to populate as
much information as it can, but if you need to override any options you're welcome to do so. You
can also write your own Dockerfile and use lambdar to build it, if you prefer.


## Config options


### `aws_account_id` and `aws_region`

Lambdar uses these when it talks to AWS. This information is needed to:

* Authenticate with AWS so lambdar can run `docker push` and upload your container.
* Construct the URL of your ECR (Elastic Container Registry) repository, which is where your
  container will be stored.
* Create the lambda function from your container (this isn't implemented yet).

If you don't supply this information you can still build a container if you have Docker installed,
or build a Dockerfile if you don't.

``` yaml
# _lambdar.yml

aws_account_id: "123456789012"

aws_region: "ap-southeast-2"
```


### `app_name`

This is used to name (via `docker tag`) your container when it's built. It also forms part of the
ECR repository URL.

``` yaml
# _lambdar.yml

app_name: "my-first-lambdar-app"
```


### `r_version`

This tells lambdar what version of R to install in your container. Lambdar pre-fills this with your
current R version, but you can change it if you need to. Make sure you specify all three digits of
the version number, e.g. `"3.6.3"`.

``` yaml
# _lambdar.yml

r_version: "4.1.1"
```


### `include_files`

If your lambda depends on additional data or code files you need to add them to the`include_files`
array. By default only files containing `@lambdar`-tagged functions will be included.

``` yaml
# _lambdar.yml

include_files: [ "main.R", "data.csv", "utils/helpers.R" ]
```


### `r_packages`

Any packages listed here will be installed when the container is built. Lambdar will try and
determine which packages you need using `renv::dependencies()` and will auto-fill this list.

``` yaml
# _lambdar.yml

r_packages: [ tidyverse, units ]
```

### `linux_packages`

If you need any extra system libraries installing, mention them here. The base AWS image is based on
CentOS, so packages will be installed by `yum`.

``` yaml
# _lambdar.yml

linux_packages: [ udunits2-devel ]
```
